Illustrating Good Practice in {\LaTeX}

### 2021-07-20 articles/good_practice.tex
tiny change
improved good practice article

This document is not meant to be a guide on how to use {\LaTeX}, since plenty of those already exist. Rather, what follows is an incoherent collection of examples that illustrate good practice. For more of my awesome {\LaTeX} resources, visit \url{https://github.com/nkostin4/LaTeX-templates}.

@@

\section{Awesome Circled Numbers}

\begin{figure}[H]
\centering
\begin{tikzpicture}[scale=1.6]
    \foreach \c in {0, 1, 2, 3, 4, 5, 6, 7, 8, 9}
    {
        \node at (\c,0) {\Huge\circled{\c}{TEAL}{RED}{BLACK}};
    }
\end{tikzpicture}
\caption*{Here are some cool circled numbers. The first argument is whatever is to be circled, and the second argument is the background color. The third argument is the outline color, and the fourth argument is the color of the first argument.}
\end{figure}

@@

@@

\blindtext[3]

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}[scale=0.75]
    % primary colors
    \fill[BLUE] (30:2.4) circle (4);
    \fill[RED] (150:2.4) circle (4);
    \fill[GREEN] (270:2.4) circle (4);
    % secondary colors
    \begin{scope} % red + blue = purple
        \clip (150:2.4) circle (4);
        \fill[PURPLE] (30:2.4) circle (4);
    \end{scope}
    \begin{scope} % red + green = yellow
        \clip (270:2.4) circle (4);
        \fill[YELLOW] (150:2.4) circle (4);
    \end{scope}
    \begin{scope} green + blue = teal
        \clip (30:2.4) circle (4);
        \fill[TEAL] (270:2.4) circle (4);
    \end{scope}
    % red + blue + green = white
    \begin{scope}
        \clip (30:2.4) circle (4);
        \clip (150:2.4) circle (4);
        \fill[WHITE] (270:2.4) circle (4);
    \end{scope}
\end{tikzpicture}
\end{figure}

>>>>

This document is not meant to be a guide on how to use {\LaTeX}, since plenty of those already exist. Instead, what follows is an incoherent collection of examples that illustrate good practice. For more of my awesome {\LaTeX} resources, visit \url{https://github.com/nkostin4/LaTeX-templates}.

@@

@@

\newpage

@@

\blindtext[2]

\newpage

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}[scale=0.5]
    % primary colors
    \fill[BLUE] (30:2.4) circle (4);
    \fill[RED] (150:2.4) circle (4);
    \fill[GREEN] (270:2.4) circle (4);
    % secondary colors
    \begin{scope} % red + blue = purple
        \clip (150:2.4) circle (4);
        \fill[PURPLE] (30:2.4) circle (4);
    \end{scope}
    \begin{scope} % red + green = yellow
        \clip (270:2.4) circle (4);
        \fill[YELLOW] (150:2.4) circle (4);
    \end{scope}
    \begin{scope} green + blue = teal
        \clip (30:2.4) circle (4);
        \fill[TEAL] (270:2.4) circle (4);
    \end{scope}
    % red + blue + green = white
    \begin{scope}
        \clip (30:2.4) circle (4);
        \clip (150:2.4) circle (4);
        \fill[WHITE] (270:2.4) circle (4);
    \end{scope}
\end{tikzpicture}
\end{figure}

\section{Awesome Circled Numbers and Highlighting}

Here are some cool circled numbers. The first argument is whatever is to be circled, and the \colorbox{TEAL}{second argument} is the background color. The \colorbox{PURPLE}{third argument} is the outline color, and the \colorbox{RED}{fourth argument} is color of the first argument.

\begin{figure}[H]
\captionsetup{width=0.8\textwidth,labelfont={color=BLACK,bf},textfont={color=BLACK}}
\centering
\begin{tikzpicture}[scale=1.6]
    \foreach \c in {0, 1, 2, 3, 4, 5, 6, 7, 8, 9}
    {
        \node at (\c,0) {\Huge\circled{\c}{TEAL}{PURPLE}{RED}};
    }
\end{tikzpicture}
\caption*{Isn't this cool?}
\end{figure}
